Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic: adapted to CHOP input format

### 2022-01-22 psy_peds_3_CHOP.Rmd
add to the CHOP pipeline the analysis aggregated by sex

# Save the output in a RData file. 
```{r}
site = "CHOP"
patient_count_psy_period_psy$siteid = site 
patient_count_psy_period_psy_clear$siteid = site 
bootstrapped_coefficients_df$siteid = site 
bootstrapped_fitted_df$siteid = site 
ratios_patients_with_without_psy$siteid = site 
quantile_bootstrapped_fitted$siteid = site
perc_disorder_group$siteid = site

save( ratios_patients_with_without_psy,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      quantile_bootstrapped_fitted,
      perc_disorder_group,
      file = paste0("../output/CHOP/peds_psy_aggResults_", site, ".RData"))

@@

>>>>

## Psychiatric conditions, dichotomized on patients' sex

### Count
```{r}
psy_female_counts <- read_csv("../output/CHOP/Psy-Counts-Female.csv")
psy_male_counts <- read_csv("../output/CHOP/Psy-Counts-Male.csv")

psy_female_counts <- psy_female_counts %>%
  mutate(female = Counts, 
         time_p = as.Date(paste(Year, Month, "01", sep = "-"))) %>%
  select( time_p, female)

psy_male_counts <- psy_male_counts %>%
  mutate(male = Counts, 
         time_p = as.Date(paste(Year, Month, "01", sep = "-"))) %>%
  select( time_p, male)

psy_total_counts <- psy_female_counts %>%
  inner_join( psy_male_counts)

patients_hospitalized_agg_sex <- psy_total_counts %>%
  pivot_longer(!time_p, names_to = "sex", values_to = "count_sex")

patients_hospitalized_agg_sex %>%
  ggplot(aes(x = time_p, y = count_sex, fill = sex)) +
  geom_bar(stat="identity", position = "dodge")+
  scale_fill_manual(values = cbPalette) +
  labs(y = "Counts",
       x = time_period,
       title = paste0("Patient counts per ", time_period, " aggregated by sex"),
       subtitle = "Per Sex") + 
  theme(legend.position = "bottom") + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se = TRUE, aes(colour=sex), colour= "black", size = 0.5)

@@

### Percentage

```{r}
##percentage
patients_hospitalized_agg_sex_perc <- psyCounts %>%
  left_join( patients_hospitalized_agg_sex, by = c("time_p")) %>% 
  replace_na(list(count_sex = 0))
patients_hospitalized_agg_sex_perc$percentage <- 100*patients_hospitalized_agg_sex_perc$count_sex/patients_hospitalized_agg_sex_perc$count_psy_patients
patients_hospitalized_agg_sex_perc %>%
  ggplot(aes(x = time_p, y = percentage, fill = sex)) +
  geom_bar(stat="identity", position = "dodge")+
  scale_fill_manual(values = cbPalette) +
  labs(y = "Percentage ",
       x = time_period,
       title = paste0("Patient (%) per ", time_period," aggregated by sex"),
       subtitle = "Per Sex") + 
  theme(legend.position = "bottom") + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se = TRUE, aes(colour=sex), colour= "black", size = 0.5)
```

# Save the output in a RData file. 
```{r}
site = "CHOP"
patient_count_psy_period_psy$siteid = site 
patient_count_psy_period_psy_clear$siteid = site 
bootstrapped_coefficients_df$siteid = site 
bootstrapped_fitted_df$siteid = site 
ratios_patients_with_without_psy$siteid = site 
quantile_bootstrapped_fitted$siteid = site
perc_disorder_group$siteid = site 
patients_hospitalized_agg_sex_perc$siteid = site

save( ratios_patients_with_without_psy,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      quantile_bootstrapped_fitted,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      file = paste0("../output/CHOP/peds_psy_aggResults_", site, ".RData"))
